Efficient Handling of String-Number Conversion

### 2020-04-04 final-version/main.tex
minor
remove widows and orphans

\usepackage{balance}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\hide}[1]{}
\newcommand{\tool}{{\textsf{Z3-Trau}}}
\newcommand{\dr}{\mathcal{R}}
\newcommand{\nat}{\mathbb{N}}
\newcommand{\integers}{\mathbb{Z}}
\newcommand{\todo}[1]{{\color{blue}TODO: #1}}
\newcommand{\lh}[1]{{\color{orange}Lukas: #1}}
\newcommand{\changed}[1]{{\color{blue}#1}}

@@

For ease of presentation, we  use the following toy example \changed{$$\Phi\!=\! \{``0"x\!=\! x``0", \sti{x} \!=\! \sti{y} ,|y|\!>\!|x| >1, 1000\!<\!|y| \}$$}
to explain the main ideas behind our decision procedure.  To make our terminology explicit: $\Phi$ states that \changed{$``0"$ concatenated with $x$ is the same as $x$ with $``0"$, the numeric value of the string $x$ is equivalent to that of $y$, $y$ is longer than $x$,  $y$ is longer than $1000$ characters, and $x$ is longer than 1.  Notice that $\Phi$ is satisfiable. E.g., it has a model $x=``00"$ and $y=``0^{1002}"$}.
\changed{Although this toy example is seemingly trivial, all the state-of-the-art string constraint solvers we tried (including Z3, CVC4, and Z3Str3) cannot solve it within 10 minutes. }

@@

Having made these assumptions, we may proceed follows. First, we build two PFAs $\leftA$ and $\rightA$ that encode the left and the right-hand side word term of the equality constraint $\phi_e$, respectively, by concatenating the restrictions of the individual variables. That is
\begin{eqnarray*}
\leftA \defeq& \dr(x_1)\cdot\ldots \cdot \dr(x_n)\\
\rightA \defeq& \dr(x_{n+1})\cdot\ldots \cdot \dr(x_m)
\end{eqnarray*}
The under-approximation of $\phi_e$ is then obtained as their synchronization formula
$$
\underf \dr {\phi_e} = \syncfof \leftA \rightA
$$
The correctness of the construction is stated by the lemma:
\begin{lemma}\label{lemma:eqcorrect}
$\semof {\underf \dr {\phi_e}}_{V_\dr  \cup \#V_\dr} = \encode \dr (\semof{\phi_e})$.
\end{lemma}

>>>>

\usepackage{balance}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\clubpenalty = 10000000
\widowpenalty = 10000000
\displaywidowpenalty = 1000000
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\hide}[1]{}
\newcommand{\tool}{{\textsf{Z3-Trau}}}
\newcommand{\dr}{\mathcal{R}}
\newcommand{\nat}{\mathbb{N}}
\newcommand{\integers}{\mathbb{Z}}
\newcommand{\todo}[1]{{\color{blue}TODO: #1}}
\newcommand{\lh}[1]{{\color{orange}Lukas: #1}}
\newcommand{\changed}[1]{#1}

@@

For ease of presentation, we  use the following toy example \changed{$$\Phi\!=\! \{``0"x\!=\! x``0", \sti{x} \!=\! \sti{y} ,|y|\!\!>\!\!|x| \!\!>\!\!1, 1000\!\!<\!\!|y| \}$$}
to explain the main ideas behind our decision procedure.  To make our terminology explicit: $\Phi$ states that \changed{$``0"$ concatenated with $x$ is the same as $x$ with $``0"$, the numeric value of the string $x$ is equivalent to that of $y$, $y$ is longer than $x$,  $y$ is longer than $1000$ characters, and $x$ is longer than 1.  Notice that $\Phi$ is satisfiable. E.g., it has a model $x=``00"$ and $y=``0^{1002}"$}.
\changed{Although this toy example is seemingly trivial, all the state-of-the-art string constraint solvers we tried (including Z3, CVC4, and Z3Str3) cannot solve it within 10 minutes. }

@@

Having made these assumptions, we may proceed follows. First, we build two PFAs $\leftA$ and $\rightA$ that encode the left and the right-hand side word term of the equality constraint $\phi_e$, respectively, by concatenating the restrictions of the individual variables. That is
	$$\leftA \defeq \dr(x_1)\cdot\ldots \cdot \dr(x_n)\ \ \  \rightA \defeq \dr(x_{n+1})\cdot\ldots \cdot \dr(x_m)$$

%\begin{eqnarray*}
%\leftA \defeq& \dr(x_1)\cdot\ldots \cdot \dr(x_n)\\
%\rightA \defeq& \dr(x_{n+1})\cdot\ldots \cdot \dr(x_m)
%\end{eqnarray*}
The under-approximation of $\phi_e$ is then obtained as their synchronization formula
$$
\underf \dr {\phi_e} = \syncfof \leftA \rightA
$$
The correctness of the construction is stated by the lemma:
\begin{lemma}\label{lemma:eqcorrect}
$\semof {\underf \dr {\phi_e}}_{V_\dr  \cup \#V_\dr} = \encode \dr (\semof{\phi_e})$.
\end{lemma}
